%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{multirow}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSmallSubheading}[1]{
  \item
    \textbf{#1}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textbf{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumePoint}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & \textbf{\small #2}
    \end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \multirow{3}{*}{\textbf{\Huge{Vinh Nguyen}}} & {\small Email: \texttt{\underline{\href{mailto:ngthanhvinh2000@gmail.com}{ngthanhvinh2000@gmail.com}}}}\\
   & {\small Github: \texttt{\underline{\href{https://github.com/ngthanhvinh}{https://github.com/ngthanhvinh}}}} \\
   & {\small Website: \texttt{\underline{\href{https://ngthanhvinh.github.io/}{https://ngthanhvinh.github.io/}}}} \\
   & {\small Mobile: +33 7 60 25 50 49} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ecole Polytechnique}{Palaiseau, France}
      {Bachelor of Science - Double degree in Mathematics and Computer Science}{Sep 2019 -- Jun 2022 (expected)}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {VinAI Research Lab}{Hanoi, Vietnam}
      {AI Engineer Intern}{May 2019 - Aug 2019}
      \resumeItemListStart
        \resumeItem{}
          {Collected raw data from different online sources to form a dataset called \textbf{PlasticVNOI}, which consisted of over \textbf{1000 images containing plastic bags}. Most of the images were then annotated manually, while the others were machine-annotated and human-verified.}
        \resumeItem{}
          {Integrated the \textbf{PlasticVNOI dataset} with the well-known {\href{http://host.robots.ox.ac.uk/pascal/VOC/}{\textbf{\underline{PASCAL VOC dataset}}}}, and eventually used the combined data to develop an accurate \textbf{Faster RCNN} model to detect plastic bags on many polluted streets in Vietnam.}
        \resumeItem{Utilizing: }
          {Tensorflow, OpenCV, Keras.}
        \resumeItem{Source: }
          {\href{https://github.com/ngthanhvinh/plasticbag-faster-rcnn}{\underline{\texttt{https://github.com/ngthanhvinh/plasticbag-faster-rcnn}}}.}
      \resumeItemListEnd

    \resumeSubheading
      {HUS High School for Gifted Students}{Hanoi, Vietnam}
      {Informatics Tutor}{Jan 2017 - Jan 2019}
      \resumeItemListStart
        \resumeItem{}
          {Instructed high school students to prepare for the Vietnam National Olympiad in Informatics, with the content covering from the \textbf{C/C++ programming language} to \textbf{algorithms} and \textbf{data structures}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------AWARDS AND HONORS-----------------
\section{Awards and Honors}
  \resumeSubHeadingListStart
    \resumePoint
      {\textbf{Top 5}, Vietnam Team Selection Contest in Informatics}{May 2018}
    \vspace*{-0.7cm}\resumePoint
      {\textbf{Gold Medal}, Singapore National Olympiad in Informatics}{Mar 2018}
    \vspace*{-0.7cm}\resumePoint
      {\textbf{First Prize}, Vietnam National Olympiad in Informatics}{Jan 2018}
    \vspace*{-0.7cm}\resumePoint
      {\textbf{Third Prize}, Vietnam National Olympiad in Informatics}{Jan 2017}
  \resumeSubHeadingListEnd


%--------PROJECTS------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSmallSubheading{React 2D Gameboard, HSGS Hackathon 2018}
    \resumeItemListStart
      \resumeItem{}
        {Led a team of 4 students to design the online graphical interface for several 2D math puzzles with \textbf{ReactJS}.}
      \resumeItem{Source: }
      {\href{https://github.com/ngthanhvinh/hsgs-hackathon-18}{\underline{\texttt{https://github.com/ngthanhvinh/hsgs-hackathon-18}}}.}
    \resumeItemListEnd

    \resumeSmallSubheading{SDL Tetris}
    \resumeItemListStart
      \resumeItem{}
        {A well-designed console game based on the traditional Tetris game with some modified rules.}
      \resumeItem{}
        {Implemented all logical "back-end" functions (such as scoring, rotations and left/right/down movements) for the game.}
      \resumeItem{Source: }
      {\href{https://github.com/zimportant/SDL_Tetris}{\underline{\texttt{https://github.com/zimportant/SDL\_Tetris}}}.}
    \resumeItemListEnd

    \resumeSmallSubheading{ObjTest}
    \resumeItemListStart
      \resumeItem{}
        {A web app which is able to classify the object on images.}
      \resumeItem{Utilizing: }
        {Flask back-end, React front-end, Tensorflow, VGG16 pre-trained model.}
      \resumeItem{Source: }
      {\href{https://github.com/ngthanhvinh/ObjTest}{\underline{\texttt{https://github.com/ngthanhvinh/ObjTest}}}.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \resumePoint
    {\textbf{Languages}: C/C++, Python, JavaScript, TypeScript.}{}
  \vspace*{-0.7cm}\resumePoint
    {\textbf{Technologies}: Git, React, NodeJS, Flask, Tensorflow, OpenCV, Keras.}{}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
